---
title: "HW1"
output: github_document
---

# Problem 1

```{r}

library(moderndive)

data("early_january_weather")

```

## Description of dataset

### Variables and their descriptions

*   origin

    * Weather station.
  
*   year, month day, hour

    * Time of recording.
  
*   temp, dewp

    * Temperature and dewpoint in F.
  
*   humid

    * Relative humidity.
  
*   wind_dir, wind_speed, wind_gust

    * Wind direction (in degrees), speed and gust speed (in mph).
  
*   precip

    * Precipitation, in inches.
  
*   pressure

    * Sea level pressure in millibars.
  
*   visib

    * Visibility in miles.
  
*   time_hour

    * Date and hour of the recording as a `POSIXct` date.
  
### Size of dataset

In this dataset, `nrow = 358` and `ncol = 15`.

### Mean temperature

```{r}

mean(early_january_weather$temp)

```

The mean temperature is for the dataset is 39.58 degrees.

### Scatterplot

```{r}

library(tidyverse)

ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + geom_point()

ggsave("weather_plot.pdf", height = 4, width = 6)

```

The graph shows an increase in temperature through the first weeks of January. It also shows that humidity increased as time passed.

# Problem 2

```{r}

set.seed(1)

problem2_df = tibble(
 x = rnorm(10),
 greater_than_0 = c(x > 0),
 earth_wind_fire = c("Do", "you", "remember", "the", "21st", "night", "of", "September", "!", "!"),
 government = factor(c("executive", "executive", "executive","legislative", "legislative", "legislative", "judicial", "judicial", "judicial", "judicial"))
)

problem2_df 

```
## Pulling variables and taking their means

```{r}

mean(pull(problem2_df, x))

```


```{r}

mean(pull(problem2_df, greater_than_0))

```

```{r}

mean(pull(problem2_df, earth_wind_fire))

```

```{r}

mean(pull(problem2_df, government))

```
When taking the means of the variables in the problem2_df data frame, we get a numerical value for our random sample, x, and for the logical vector, named greater_than_0. However, for the character vector and factor vector (earth_wind_fire and government), we get warning that says "qrgument is not numeric or logical: returning NA[1] NA".

```{r results = "hide", warning = FALSE}

as.numeric(pull(problem2_df, greater_than_0))
as.numeric(pull(problem2_df, earth_wind_fire))
as.numeric(pull(problem2_df, government))

```
When we use the as.numeric function on the logical, character, and factor vectors, we get set of binary numbers for the logical vector, NA for the character vector, and groupings of numbers for the factor vector. This helps to explain what happens when we try to take the mean of each vector. For the logical vector, there are binary numbers, 1 and 0, corresponding to TRUE and FALSE, that can be used to calculate a mean. For the character vector, there are no numeric values to calculate a mean from, which is why the as.numeric function returns NA. For the factor vector, each level is attributed to 1, 2, or 3. Since the levels are not numerically meaningful, a mean cannot be calculated.









