---
title: "HW1"
output: github_document
---

# Problem 1

```{r}

library(moderndive)

data("early_january_weather")

```

## Description of dataset

### Variables and their descriptions

*   origin

    * Weather station.
  
*   year, month day, hour

    * Time of recording.
  
*   temp, dewp

    * Temperature and dewpoint in F.
  
*   humid

    * Relative humidity.
  
*   wind_dir, wind_speed, wind_gust

    * Wind direction (in degrees), speed and gust speed (in mph).
  
*   precip

    * Precipitation, in inches.
  
*   pressure

    * Sea level pressure in millibars.
  
*   visib

    * Visibility in miles.
  
*   time_hour

    * Date and hour of the recording as a `POSIXct` date.
  
### Size of dataset

In this dataset, `nrow = 358` and `ncol = 15`.

### Mean temperature

```{r}

mean(early_january_weather$temp)

```

The mean temperature is for the dataset is 39.58 degrees.

### Scatterplot

```{r}

library(tidyverse)

ggplot(early_january_weather, aes(x = time_hour, y = temp, colour = humid)) + geom_point()

ggsave("weather_plot.pdf", height = 4, width = 6)

```

The graph shows an increase in temperature through the first weeks of January. It also shows that humidity increased as time passed.

# Problem 2

```{r}

set.seed(1)

problem2_df = tibble(
 x = rnorm(10),
 vec_logical = c(x > 0),
 vec_char = c("Do", "you", "remember", "the", "21st", "night", "of", "September", "!", "!"),
 vec_factor = factor(c("executive", "executive", "executive","legislative", "legislative", "legislative", "judicial", "judicial", "judicial", "judicial"))
)

problem2_df

```





